Master Thesis

### 2013-05-15 acg.tex
First reading/revision of section I

\begin{figure}
  \begin{prooftree}
    \AxiomC{$\emptyset, \Gamma_i \vdash_\Sigma c : \tau(c)$ (cons)}
  \end{prooftree}
  \begin{prooftree}
    \AxiomC{$(x : \alpha), \Gamma_i \vdash_\Sigma x : \alpha$ (l-var)}
  \end{prooftree}
  \begin{prooftree}
    \AxiomC{$\emptyset, (\Gamma_i, x : \alpha) \vdash_\Sigma x : \alpha$ (i-var)}
  \end{prooftree}
  \begin{prooftree}
    \AxiomC{$(\Gamma_l, x : \alpha), \Gamma_i \vdash_\Sigma t : \beta$}
    \RightLabel{(l-abs)}
    \UnaryInfC{$\Gamma_l, \Gamma_i \vdash_\Sigma \lambda^{\circ} x. t : \alpha \limp \beta$}
  \end{prooftree}
  \begin{prooftree}
    \AxiomC{$\Gamma_l, (\Gamma_i, x : \alpha) \vdash_\Sigma t : \beta$}
    \RightLabel{(i-abs)}
    \UnaryInfC{$\Gamma_l, \Gamma_i \vdash_\Sigma \lambda x. t : \alpha \to \beta$}
  \end{prooftree}
  \begin{prooftree}
    \AxiomC{$\Gamma_l, \Gamma_i \vdash_\Sigma t : \alpha \limp \beta$}
    \AxiomC{$\Delta_l, \Delta_i \vdash_\Sigma u : \alpha$}
    \RightLabel{(l-app)}
    \BinaryInfC{$(\Gamma_l, \Delta_l), (\Gamma_i, \Delta_i) \vdash_\Sigma (t\ u) : \beta$}
  \end{prooftree}
  \begin{prooftree}
    \AxiomC{$\Gamma_l, \Gamma_i \vdash_\Sigma t : \alpha \to \beta$}
    \AxiomC{$\emptyset, \Delta_i \vdash_\Sigma u : \alpha$}
    \RightLabel{(i-app)}
    \BinaryInfC{$\Gamma_l, (\Gamma_i, \Delta_i) \vdash_\Sigma (t\ u) : \beta$}
  \end{prooftree}
  \caption{\label{fig:type-judgments} Type judgment schemas of the
    well-typed lambda terms $\Lambda(\Sigma)$ for a signature $\Sigma =
    \mathopen{<}A, C, \tau\mathclose{>}$}
\end{figure}

@@

An abstract categorial grammar for us will then be just a collection of
signatures with their distinguished types and lexicons connecting these
signatures. A common pattern will have us using two signatures for the
surface forms of utterances (strings) and their logical forms (logical
propositions) and an abstract signature which is connected to both of
the object signatures via lexicons. Parsing is then just a matter of
inverting the surface lexicon to get the abstract term and then applying
to it the logical lexicon. Generation is symmetric, we simply invert the
logical lexicon and apply the surface lexicon.

@@

So, how does our lexicon $\mathcal{L}_{syntax}$ look like? It will map
all the atomic types of $\Sigma_{Synt}$ into $\textsc{String}$, which we
can write as $\mathcal{L}_{syntax}(n) = \mathcal{L}_{syntax}(np) =
\mathcal{L}_{syntax}(s)$\footnote{Whenever we talk about some lexicon,
  we will use the lexicon itself, which is formally a pair of mappings
  $\mathopen{<}F, G\mathclose{>}$, to mean either $F$, $G$ or their
  homomorphic extensions $\hat{F}$ and $\hat{G}$ depending on whether
  the argument is an atomic type, a constant, a complex type or a term
  respectively.}. From that, we can use the homomorphic extension of our
type mapping to arrive at the object-level interpretations of complex
types, such as the type of predicates, $np \limp s$, which becomes a
unary string function, $\textsc{String} \limp \textsc{String}$, or the
type of quantified noun phrases, $(np \limp s) \limp s$, which becomes a
higher-order string function, $(\textsc{String} \limp \textsc{String})
\limp \textsc{String}$. With the types out of the way, we can give the
interpretation of the individual constants of $\Sigma_{Synt}$:
\begin{itemize}
\item $\mathcal{L}_{syntax}(\synt{every}) = \lambda^{\circ} x
  R.\ R\ (every\ +\ x)$
\item $\mathcal{L}_{syntax}(\synt{some}) = \lambda^{\circ} x
  R.\ R\ (some\ +\ x)$
\item $\mathcal{L}_{syntax}(\synt{love}) = \lambda^{\circ} x
  y.\ x\ +\ loves\ +\ y$
\item $\mathcal{L}_{syntax}(\synt{man}) = man$
\item $\mathcal{L}_{syntax}(\synt{woman}) = woman$
\end{itemize}

We can now go back to our examples from $\Lambda(\Sigma_{Synt})$ and
look at what they look like after applying the lexicon to them.
\begin{itemize}
\item $t_3 = \synt{some}\ \synt{woman}$ \\ Mapping this term using the
  lexicon and $\beta$-reducing gives us $\mathcal{L}_{syntax}(t_3)
  =_{\beta} \lambda^{\circ} R.\ R\ (some\ +\ woman)$, which is a
  type-raised version of the string \emph{some woman}.
\item $t_4 = \lambda^{\circ}
  x.\ (\synt{some}\ \synt{woman})\ (\lambda^{\circ}
  y.\ \synt{love}\ x\ y)$ \\ Our verb phrase ends up being mapped onto
  a function which appends the phrase \emph{loves some woman} to its
  argument, $\mathcal{L}_{syntax}(t_4) =_{\beta} \lambda^{\circ}
  x.\ x\ +\ loves\ +\ some\ +\ woman$
\item $t_5 = (\synt{every}\ \synt{man})\ (\lambda^{\circ}
  x.\ (\synt{some}\ \synt{woman})\ (\lambda^{\circ}
  y.\ \synt{love}\ x\ y))$ \\ Finally, the sentence (type $s$) is mapped
  into a simple $\textsc{String}$, $\mathcal{L}_{syntax}(t_5) =_{\beta}
  every\ +\ man\ +\ loves\ +\ some\ +\ woman$.
\end{itemize}

Now we have enough machinery in play to define the set of strings which
form our fragment of English. We will consider the \emph{abstract
  language} generated by our signature $\Sigma_{Synt}$ and the
distinguished type $s$, that is, elements of $\Lambda(\Sigma_{Synt})$
having type $s$. Then we can define the \emph{object language}, which is
the image of the abstract language when transformed using the
lexicon. The object language contains strings, terms from
$\Lambda(\Sigma_{String})$ having the type $\textsc{String}$. However,
the object language does not contain all such terms, but only those
object terms, for which there exists a term in the abstract language
such that its image given by the lexicon yields the same object term.

>>>>

\begin{figure}
  \begin{prooftree}
    \AxiomC{$\emptyset; \Gamma_i \vdash_\Sigma c : \tau(c)$ (cons)}
  \end{prooftree}
  \begin{prooftree}
    \AxiomC{$(x : \alpha); \Gamma_i \vdash_\Sigma x : \alpha$ (l-var)}
  \end{prooftree}
  \begin{prooftree}
    \AxiomC{$\emptyset; (\Gamma_i, x : \alpha) \vdash_\Sigma x : \alpha$ (i-var)}
  \end{prooftree}
  \begin{prooftree}
    \AxiomC{$(\Gamma_l, x : \alpha); \Gamma_i \vdash_\Sigma t : \beta$}
    \RightLabel{(l-abs)}
    \UnaryInfC{$\Gamma_l; \Gamma_i \vdash_\Sigma \lambda^{\circ} x. t : \alpha \limp \beta$}
  \end{prooftree}
  \begin{prooftree}
    \AxiomC{$\Gamma_l; (\Gamma_i, x : \alpha) \vdash_\Sigma t : \beta$}
    \RightLabel{(i-abs)}
    \UnaryInfC{$\Gamma_l; \Gamma_i \vdash_\Sigma \lambda x. t : \alpha \to \beta$}
  \end{prooftree}
  \begin{prooftree}
    \AxiomC{$\Gamma_l; \Gamma_i \vdash_\Sigma t : \alpha \limp \beta$}
    \AxiomC{$\Delta_l; \Delta_i \vdash_\Sigma u : \alpha$}
    \RightLabel{(l-app)}
    \BinaryInfC{$(\Gamma_l, \Delta_l); (\Gamma_i, \Delta_i) \vdash_\Sigma (t\ u) : \beta$}
  \end{prooftree}
  \begin{prooftree}
    \AxiomC{$\Gamma_l; \Gamma_i \vdash_\Sigma t : \alpha \to \beta$}
    \AxiomC{$\emptyset; \Delta_i \vdash_\Sigma u : \alpha$}
    \RightLabel{(i-app)}
    \BinaryInfC{$\Gamma_l; (\Gamma_i, \Delta_i) \vdash_\Sigma (t\ u) : \beta$}
  \end{prooftree}
  \caption{\label{fig:type-judgments} Type judgment schemas of the
    well-typed lambda terms $\Lambda(\Sigma)$ for a signature $\Sigma =
    \mathopen{<}A, C, \tau\mathclose{>}$}
\end{figure}

@@

An abstract categorial grammar for us will then be just a collection of
signatures with their distinguished types and lexicons connecting these
signatures. A common pattern will have us using two object signatures
for the surface forms of utterances (strings) and their logical forms
(logical propositions) and an abstract signature which is connected to
both of the object signatures via lexicons. Parsing is then just a
matter of inverting the surface lexicon to get the abstract term and
then applying to it the logical lexicon. Generation is symmetric, we
simply invert the logical lexicon and apply the surface lexicon.

@@

So, how does our lexicon $\mathcal{L}_{syntax}$ look like? It will map
all the atomic types of $\Sigma_{Synt}$ into $\textsc{String}$, which we
can write as $\mathcal{L}_{syntax}(n) = \mathcal{L}_{syntax}(np) =
\mathcal{L}_{syntax}(s) = \textsc{String}$\footnote{Whenever we talk
  about some lexicon, we will use the lexicon itself, which is formally
  a pair of mappings $\mathopen{<}F, G\mathclose{>}$, to mean either
  $F$, $G$ or their homomorphic extensions $\hat{F}$ and $\hat{G}$
  depending on whether the argument is an atomic type, a constant, a
  complex type or a term respectively.}. From that, we can use the
homomorphic extension of our type mapping to arrive at the object-level
interpretations of complex types, such as the type of predicates, $np
\limp s$, which becomes a unary string function, $\textsc{String} \limp
\textsc{String}$, or the type of quantified noun phrases, $(np \limp s)
\limp s$, which becomes a higher-order string function,
$(\textsc{String} \limp \textsc{String}) \limp \textsc{String}$. With
the types out of the way, we can give the interpretation of the
individual constants of $\Sigma_{Synt}$:
\begin{itemize}
\item $\mathcal{L}_{syntax}(\synt{every}) = \lambda^{\circ} x
  R.\ R\ (every\ +\ x)$
\item $\mathcal{L}_{syntax}(\synt{some}) = \lambda^{\circ} x
  R.\ R\ (some\ +\ x)$
\item $\mathcal{L}_{syntax}(\synt{love}) = \lambda^{\circ} x
  y.\ x\ +\ loves\ +\ y$
\item $\mathcal{L}_{syntax}(\synt{man}) = man$
\item $\mathcal{L}_{syntax}(\synt{woman}) = woman$
\end{itemize}

We can now go back to our examples from $\Lambda(\Sigma_{Synt})$ and
look at what they look like after applying the lexicon to them.
\begin{itemize}
\item $t_3 = \synt{some}\ \synt{woman}$ \\ Mapping this term using the
  lexicon and $\beta$-reducing gives us $\mathcal{L}_{syntax}(t_3)
  =_{\beta} \lambda^{\circ} R.\ R\ (some\ +\ woman)$, which is a
  type-raised version of the string \emph{some woman}.
\item $t_4 = \lambda^{\circ}
  x.\ (\synt{some}\ \synt{woman})\ (\lambda^{\circ}
  y.\ \synt{love}\ x\ y)$ \\ Our verb phrase ends up being mapped onto
  a function which appends the phrase \emph{loves some woman} to its
  argument, $\mathcal{L}_{syntax}(t_4) =_{\beta} \lambda^{\circ}
  x.\ x\ +\ loves\ +\ some\ +\ woman$.
\item $t_5 = (\synt{every}\ \synt{man})\ (\lambda^{\circ}
  x.\ (\synt{some}\ \synt{woman})\ (\lambda^{\circ}
  y.\ \synt{love}\ x\ y))$ \\ Finally, the sentence (type $s$) is mapped
  into a simple $\textsc{String}$, $\mathcal{L}_{syntax}(t_5) =_{\beta}
  every\ +\ man\ +\ loves\ +\ some\ +\ woman$.
\end{itemize}

Now we have enough machinery in play to define the set of strings which
form our fragment of English. We will consider the \emph{abstract
  language} generated by our signature $\Sigma_{Synt}$ and the
distinguished type $s$, that is, elements of $\Lambda(\Sigma_{Synt})$
having type $s$. Then we can define the \emph{object language}, which is
the image of the abstract language when transformed using the
lexicon. The object language contains strings, terms from
$\Lambda(\Sigma_{String})$ having the type $\textsc{String}$. However,
the object language does not contain all such terms, but only those
object terms, for which there exists a term in the abstract language
such that its image given by the lexicon yields the same object term,
i.e. it contains only terms which denote strings that spell out
sentences of our fragment of English.

### 2013-05-15 ig.tex
First reading/revision of section I

We will briefly discuss one more grammar formalism and that is the
formalism of Interaction Grammars \cite{guillaume2009interaction}.
Interaction grammars are a grammatical formalism centered around the
concept of \emph{polarity}. An interaction grammar is a set of
(underspecified) tree descriptions which define a set of trees that can
be constructed by superposing some of these tree descriptions while
respecting the polarities described in the nodes of the individual tree
descriptions.

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.25]{ig-parse.pdf}
  \caption{\label{fig:ig-parse} Syntactic tree of sentence
    (\ref{ex:ig}). The numbers at the top of the nodes are labels of
    nodes from the elementary polarized tree descriptions that generated
    the syntactic tree (see Figure \ref{fig:ig-eptds}).}
\end{figure}

Figure \ref{fig:ig-parse} shows the syntactic tree assigned by Frigram
to the sentence in (\ref{ex:ig}). It is a rooted ordered tree with the
topmost node being the root. Solid lines indicate immediate dominance
with the higher node being the parent and the lower the child. The
ordering of children is given by the arrows, which signify the immediate
precedence relation between sister nodes.

@@

Interaction grammars are a formalism enabling us to define sets of the
structures described above, the \emph{syntactic trees}. Similar to Tree
Adjoining Grammars, interaction grammars are formulated in terms of a
set of elementary structures which can combine to produce the final
output structures. However, unlike in tree adjoining grammars, the
output structure is not constructed from the elementary structures via
some set of algebraic operations (substitution and adjunction in case of
TAG). Instead, \emph{polarized tree descriptions} (PTDs), the elementary
structures of interaction grammars, impose constraints on the final
structure and a structure is said to be generated by some PTDs if it is
a minimal structure satisfying those constraints (it is a \emph{minimal
  model}).

@@

The clitic pronoun $la$ participates in the positive/negative resource
management system as well, since using the clitic fills up the object
slot in the valency of a verb. The EPTD of $la$ also relies heavily on
virtual features and uses them to specify in more detail the context in
which this rule is applicable, so as to avoid over-generation.

Now that we understand the constraints imposed by PTDs, we can start to
see that the syntactic tree in Figure~\ref{fig:ig-parse} is truly a
model of the PTDs given in Figure~\ref{fig:ig-eptds} and more than that,
it is the only minimal model. To illustrate more clearly how the
polarities and constraints of the individual PTDs end up generating the
syntactic tree of Figure~\ref{fig:ig-parse}, we can look at the result
of superposing the EPTDs of $la$ and $voit$ by merging the nodes (1,2)
and (1,5) with (2,2) and (2,4) respectively on
Figure~\ref{fig:ig-partial}.

@@

However, defining some 4000 EPTDs manually still seems like a very
tedious, error prone and hard to maintain approach. Many of the EPTDs
have to repeatedly describe common phenomena such as subject-object
agreement or predicate-argument saturation. Similarly as in other
software endeavors, it would be preferable to define these common
patterns in some reusable module and compose EPTDs from these building
blocks. This is where XMG steps in.

@@

With the added capability of composing classes, the definition of
Frigram reduces to about 400 class definitions. Of these classes, 160
are terminal, meaning that they actually describe lexical items that are
to be included in the final grammar. Thanks to the disjunction
composition operator of XMG, these 160 classes end up generating the
staggering 4000 EPTDs.

@@

This symmetry turns Perrier's theorem into a strong claim that lets us
transform the types of a signature into elementary syntactic
descriptions such that some selection of descriptions will generate some
tree if and only if the selection of the corresponging typed constants
generated some properly-typed term. Inverting this transformation would
then let us take the elementary syntactic descriptions of an IG like
Frigram and turn them into types for an abstract signature of our ACG.

@@

While this property may not hold for the PTDs we find in Frigram, it
still gives us a general plan for recovering IILL types. The strategy
suggested by the description-formula connection given by the theorem
yields a mapping $F$ from the under-specified trees to IILL formulas.

@@

This strategy corresponds to our intuitions about tree descriptions
should be expressed using IILL types. We will consider two very simple
cases to demonstrate it.

@@

Once again, at the root of the EPTD we see the modifier pattern in
action. If we take the subtree formed by the nodes (2,8) and (2,9) to
represent a modification of some constituent, say a noun, then we get a
type like $n \limp n$. However, the EPTD contains also positive and
negative $cat$ polarities. The node (2,0) has a negative $cat$ polarity
and we can consider it as an argument, meaning that the type we would
like to derive would look like $F((2,0)) \limp (n \limp n)$. Our
strategy $F$ has nothing to say about virtual features or (large)
dominance constraints. If we look only at the positive and negative
$cat$ features, $F((2,0))$ becomes $np \limp s$, which would give us
$(np \limp s) \limp (n \limp n)$ as the final type.

However, this translation is very lossy in terms of its discriminatory
power. Many of the constraints which were forced by the original EPTD
are now ignored. We can imagine boosting our strategy by using the
feature structures as our types instead of atomic categories, which
would not only ensure that e.g. the $sent\_type$ of the embedded clause
must be $decl$, but would also capture the information in the polarized
$funct$ feature so that the relative pronoun $que$ is not permitted to
extract subjects. There are still constraints that we would miss out
though, such as the fact that the subject (2,3) of the clause (2,0) must
precede any embedded clauses (2,6)...(2,5), the fact that any such
embedded clause must serve either the $modal$ or the $obj$ function and
the fact that the embedded clause (2,5) must have a subject (2,4).

Other constraints that we did not mention also do not have a direct
equivalent in ACGs. One example would be a feature of IGs that we have
not even mentioned which allows us the grammar author to provide an
\emph{exhaustive} list of children of a node in a PTD. Another kind of
tricky constraint are the orange rectangles that we can see in
Figure~\ref{fig:ig-que} which enforce that a constituent must be the
left-most or right-most daughter. The problem with these is similar as
with precedence relations. To model their impact on word order would be
easy using an ACG lexicon, but to model their effect on restricting
syntactic composition would be more tricky.

In the end, even though both formalisms (IGs and ACGs) are built on the
framework of linear logic and their fundamental principles of syntactic
composition have been linked together by Perrier's theorem, we conclude
that embedding Frigram into an ACG or constructing some automated
technique for translating the Frigram EPTDs into ACG types and terms
would not be feasible. Perhaps using some of the other connectives of
linear logic would allows us to model the Frigram EPTDs, and the ways
they manipulate multiple resources at the same time, in a more efficient
manner. However, this would lead us well out of the framework of ACGs in
which we wish to conduct our research.

In our grammar, we will still gladly use the lexicon Frilex, which
proves the usefulness of clearly defining the interface between the
lexicon from the grammar in the architecture of Frigram. In our grammar,
Frigram can still serve as a guide on how to interface with Frilex, on
which phenomena need to be covered and in what detail, and what is a
good way to structure the reusable components of a grammar of French.

>>>>

We will briefly discuss one more grammar formalism and that is the
formalism of Interaction Grammars \cite{guillaume2009interaction}.
Interaction grammars are a grammatical formalism centered around the
concept of \emph{polarity}. An interaction grammar is a set of
(under-specified) tree descriptions which define a set of trees that can
be constructed by superposing some of these tree descriptions while
respecting the polarities described in the nodes of the individual tree
descriptions.

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.25]{ig-parse.pdf}
  \caption{\label{fig:ig-parse} The syntactic tree of sentence
    (\ref{ex:ig}). The numbers at the top of the nodes are labels of
    nodes from the elementary polarized tree descriptions that generated
    the syntactic tree (see Figure \ref{fig:ig-eptds}).}
\end{figure}

Figure \ref{fig:ig-parse} shows the syntactic tree assigned by Frigram
to sentence (\ref{ex:ig}). It is a rooted ordered tree with the topmost
node being the root. Solid lines indicate immediate dominance with the
higher node being the parent and the lower the child. The ordering of
children is given by the arrows, which signify the immediate precedence
relation between sister nodes.

@@

Interaction grammars are a formalism enabling us to define sets of the
structures described above, the \emph{syntactic trees}. Similar to tree
adjoining grammars, interaction grammars are formulated in terms of a
set of elementary structures which can combine to produce the final
output structures. However, unlike in tree adjoining grammars, the
output structure is not constructed from the elementary structures via
some set of algebraic operations (substitution and adjunction in case of
TAG). Instead, \emph{polarized tree descriptions} (PTDs), the elementary
structures of interaction grammars, impose constraints on the final
structure and a structure is said to be generated by some PTDs if it is
a minimal structure satisfying those constraints (it is a \emph{minimal
  model}). This distinction separates TAG as a formalism in the
generative-enumerative framework of syntax with IG as a formalism in the
model-theoretic framework.

@@

The clitic pronoun $la$ participates in the positive/negative resource
management system as well, since using the clitic fills up the object
slot in the valency of a verb. The EPTD of $la$ also uses virtual
features heavily to select the right place where to hang the pronoun.

Now that we understand the constraints imposed by PTDs, we can start to
see that the syntactic tree in Figure~\ref{fig:ig-parse} is truly a
model of the PTDs given in Figure~\ref{fig:ig-eptds} (furthermore, it is
the only minimal model). To illustrate more clearly how the polarities
and constraints of the individual PTDs end up generating the syntactic
tree of Figure~\ref{fig:ig-parse}, we can look at the result of
superposing the EPTDs of $la$ and $voit$ by merging the nodes (1,2) and
(1,5) with (2,2) and (2,4) respectively on Figure~\ref{fig:ig-partial}.

@@

However, defining some 4000 EPTDs manually still seems like a very
tedious, error prone and hard to maintain process. Many of the EPTDs
have to repeatedly describe common phenomena such as subject-predicate
agreement or predicate-argument saturation. Similarly as in other
software endeavors, it would be preferable to define these common
patterns in some reusable module and compose EPTDs from these building
blocks. This is where XMG steps in.

@@

With the added capability of composing classes, the definition of
Frigram reduces to about 400 class definitions. Of these classes, 160
are terminal, meaning that they actually describe lexical items that are
to be included in the final grammar. Thanks to the disjunction
composition operator of XMG, these 160 classes end up generating the
4000 EPTDs.

@@

This symmetry turns Perrier's theorem into a strong claim that lets us
transform the types of a signature into elementary syntactic
descriptions such that some selection of descriptions will generate some
tree if and only if the selection of the corresponding typed constants
generated some properly typed term. Inverting this transformation would
then let us take the elementary syntactic descriptions of an IG like
Frigram and turn them into types for an abstract signature of our ACG.

@@

While this property may not hold for the PTDs we find in Frigram, it
still gives us a general plan for recovering IILL types. The strategy
suggested by the description/formula connection given by the theorem
yields a mapping $F$ from the under-specified trees to IILL formulas.

@@

This strategy corresponds to our intuitions about how should tree
descriptions be expressed using IILL types. We will consider two very
simple cases to demonstrate it.

@@

Once again, at the root of the EPTD we see the modifier pattern in
action. If we take the subtree formed by the nodes (2,8) and (2,9) to
represent a modification of some constituent, say a noun, then we get a
type like $n \limp n$. However, the EPTD contains also positive and
negative $cat$ polarities. The node (2,0) has a negative $cat$ polarity
and we can consider it as an argument, meaning that the type we would
like to derive would look like $F((2,0)) \limp (n \limp n)$. However,
our strategy $F$ has nothing to say about virtual features or (large)
dominance constraints, so we will have to ignore those. If we look only
at the positive and negative $cat$ features, $F((2,0))$ becomes $np
\limp s$, which would give us $(np \limp s) \limp (n \limp n)$ as the
final type.

However, this translation is very lossy in terms of its discriminatory
power. Many of the constraints which were forced by the original EPTD
are now ignored. We can imagine improving our strategy by using the
feature structures as our types instead of atomic categories, which
would not only ensure that e.g. the $sent\_type$ of the embedded clause
must be $decl$, but would also capture the information in the polarized
$funct$ feature so that the relative pronoun $que$ is not permitted to
extract subjects. There are still constraints that we would miss out on
though, such as the fact that the subject (2,3) of the clause (2,0) must
precede any embedded clauses (2,6)...(2,5), the fact that any such
embedded clause must serve either the $modal$ or the $obj$ function and
the fact that the embedded clause (2,5) must have a subject (2,4).

Other constraints that we did not mention also do not have a direct
equivalent in ACGs. One example would be a feature of IGs that we have
not even mentioned which allows us the grammar author to provide an
\emph{exhaustive} list of children of a node in a PTD. Another kind of
tricky constraint are the orange rectangles that we can see in
Figure~\ref{fig:ig-que} which enforce that a constituent must be the
leftmost or rightmost daughter of its parent. The problem with these is
similar as with precedence relations. To model their impact on word
order would be easy using an ACG lexicon, but to model their effect on
restricting syntactic composition would be more tricky.

In the end, even though both formalisms (IGs and ACGs) are built on the
framework of linear logic and their fundamental principles of syntactic
composition have been linked together by Perrier's theorem, we conclude
that embedding Frigram into an ACG or constructing some automated
technique for translating the Frigram EPTDs into ACG types and terms
would not be feasible. We suspect that the incompatibility of these two
formalisms is due to ACG being a formalism based in the
generative-enumerative framework of syntax while IG is based in the
model-theoretic approach. Perhaps we could model the operational view of
IG, the combination of under-specified trees via superposition, by
employing some of the other connectives of linear logic to model the
fact that superposing PTDs usually involves many resources. However,
this would lead us well out of the framework of ACGs in which we wish to
conduct our research because of its elegant approach to discourse
denotations.

In our grammar, we will still gladly use the lexicon Frilex though,
which proves the usefulness of clearly defining the interface between
the lexicon and the grammar in the architecture of Frigram. In our
grammar, Frigram can still serve as a guide on how to interface with
Frilex, on which phenomena need to be covered and in what detail, and
what is a good way to structure the reusable components of a grammar of
French.

### 2013-05-15 motivation.tex
First reading/revision of section I

The discourse in (\ref{salmon}) and its structure in (TODO) demonstrate
another feature of discourse structures. First off, seeing the
hiearchical structure of the discourse gives us important information
about the granularity of the descriptions given in the individual
propositions, information that could be useful for performing tasks such
as text summarization.

>>>>

The discourse in (\ref{salmon}) and its structure in (TODO) demonstrate
another feature of discourse structures. First off, seeing the
hierarchical structure of the discourse gives us important information
about the granularity of the descriptions given in the individual
propositions, information that could be useful for performing tasks such
as text summarization.
